\documentclass[12pt,a4paper]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{hyperref}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric}

\setmainfont{Times New Roman}
% Prefer Microsoft JhengHei per the report requirements; fall back to
% Heiti TC when compiling on a machine without the Microsoft font.
\IfFontExistsTF{Microsoft JhengHei}
  {\newfontfamily\chinesefont{Microsoft JhengHei}}
  {\newfontfamily\chinesefont{Heiti TC}}
\singlespacing
\setlength{\parindent}{1.5em}
\setlength{\parskip}{0pt}
\setlist{nosep,leftmargin=1.8em}
\setcounter{secnumdepth}{2}
\pagestyle{plain}

\definecolor{farblue}{HTML}{2F6B9A}
\definecolor{nearorange}{HTML}{C56A22}
\definecolor{polarred}{HTML}{B8423F}
\definecolor{darkgreen}{HTML}{347A57}
\definecolor{softgray}{HTML}{F1F3F5}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  urlcolor=farblue,
  pdftitle={Channel Estimation for Extremely Large-Scale MIMO},
  pdfauthor={Group 1}
}

\newcommand{\fieldvec}[1]{\boldsymbol{#1}}
\newcommand{\tightsection}[1]{\section{#1}\vspace{-0.35em}}
\newcommand{\infofield}[2]{\textbf{#1:} #2\hfill}

\begin{document}

% ---------------------------------------------------------------------------
% Page 1: Motivation and channel models
% ---------------------------------------------------------------------------
\begin{center}
  {\Large\bfseries Channel Estimation for Extremely Large-Scale MIMO:\\
  Far-Field or Near-Field?}

  \vspace{0.55em}
  \infofield{Course}{Principles of Wireless Communications}\\[0.35em]
  \infofield{Student}{{\chinesefont
  朱昱安、何傳盛、楊予綸、柯均儒、陳楷寰、王郁仁}}\\[0.35em]
  \infofield{Instructor}{Prof. Shih-Chun Lin}
  \infofield{Date}{2026/06/09}
\end{center}

\vspace{-0.45em}
\tightsection{Motivation}

Extremely large-scale multiple-input multiple-output (XL-MIMO) uses
hundreds of antennas to provide the array gain and spatial resolution
needed for high-rate 6G links. Accurate channel state information is
essential for precoding, yet the number of radio-frequency chains is much
smaller than the number of antennas. Directly estimating every antenna
coefficient would therefore require excessive pilot overhead.

Compressed sensing reduces this overhead by assuming that only a few paths
are active in an angular Fourier dictionary. Cui and Dai show that this
assumption breaks down when the XL-MIMO aperture places users or scatterers
in the near field \cite{cui2022}.

\tightsection{Far-Field and Near-Field Propagation}

The boundary is approximated by the Rayleigh distance
\begin{equation}
  Z=\frac{2D^2}{\lambda},
  \label{eq:rayleigh}
\end{equation}
where $D$ is the array aperture and $\lambda$ is the wavelength. Since
$Z$ grows quadratically with $D$, an XL-MIMO array can have a near-field
region extending over a large part of a cell.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[
      >=Latex,
      antenna/.style={draw,fill=black,minimum width=0.07cm,minimum height=0.42cm},
      terminal/.style={draw,rounded corners,minimum width=0.7cm,minimum height=1.0cm},
      note/.style={font=\small,align=center}
    ]
    \foreach \x in {0,0.32,...,2.88} \node[antenna] at (\x,0) {};
    \node[note] at (1.44,-0.52) {XL-MIMO array};
    \node[terminal,fill=nearorange!10] (near) at (5.0,0.65) {near};
    \node[terminal,fill=farblue!10] (far) at (10.8,0.65) {far};
    \foreach \y in {-0.15,0.05,0.25}
      \draw[nearorange,thick] (3.0,\y) to[bend left=14] (near.west);
    \foreach \y in {-0.15,0.05,0.25}
      \draw[farblue,thick] (3.0,\y) -- (far.west);
    \draw[dashed] (7.7,-0.65) -- (7.7,1.45);
    \node[note,nearorange] at (5.0,1.55)
      {spherical wave\\angle $\theta$ and distance $r$};
    \node[note,farblue] at (10.8,1.55)
      {planar wave\\angle $\theta$ only};
    \node[note] at (7.7,-0.9) {Rayleigh boundary};
  \end{tikzpicture}
  \caption{Propagation models emphasized in the group presentation.}
  \label{fig:fields}
\end{figure}

Far-field phase changes linearly across the array, so one Fourier vector
$\fieldvec{a}(\theta)$ is sufficient. Near-field phase also depends on
distance and requires $\fieldvec{b}(\theta,r)$. An angle-only dictionary
therefore spreads one physical near-field path over many bins.

\tightsection{Paper Contributions}

The paper restores sparsity with a polar dictionary that samples angle and
distance, then proposes P-SOMP for on-grid recovery and P-SIGW for off-grid
refinement. The key question is which coordinates preserve physical
sparsity.

\newpage

% ---------------------------------------------------------------------------
% Page 2: Polar-domain representation
% ---------------------------------------------------------------------------
\tightsection{Near-Field Channel Model}

For a uniform linear array with antenna index $n=0,1,\ldots,N-1$,
spacing $d$, and wavenumber $k_c=2\pi/\lambda$, the near-field steering
vector is
\begin{equation}
  \fieldvec{b}(\theta,r)
  =\frac{1}{\sqrt{N}}
  \left[e^{-jk_c(r^{(0)}-r)},\ldots,
        e^{-jk_c(r^{(N-1)}-r)}\right]^{T},
  \label{eq:steering}
\end{equation}
where
\begin{equation}
  r^{(n)}=\sqrt{r^2+\delta_n^2d^2-2r\delta_n d\theta},
  \qquad \delta_n=\frac{2n-N+1}{2},
  \label{eq:distance}
\end{equation}
is the distance between the source and the $n$-th antenna located at
$\delta_n d$, and $\theta\in[-1,1]$ is the spatial angle. Unlike a
Fourier vector, Equation~\eqref{eq:steering} has a nonlinear phase
progression that changes with both $\theta$ and $r$.

With a limited number of paths, the channel remains compressible even
though it is not sparse in angle. The proposed representation is
\begin{equation}
  \fieldvec{h}_m=\fieldvec{W}\fieldvec{h}^{P}_m,
  \label{eq:polar}
\end{equation}
where every column of $\fieldvec{W}$ is a sampled steering vector
$\fieldvec{b}(\theta_p,r_p)$ and $\fieldvec{h}^{P}_m$ is sparse in the
polar domain. The subscript $m$ denotes a subcarrier; the path locations
are shared across subcarriers, which enables simultaneous recovery.

\tightsection{From Energy Spread to Polar Sparsity}

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[x=0.72cm,y=2.2cm,font=\small,scale=0.95,transform shape]
    % Left axes
    \draw[->] (0,0) -- (7.2,0) node[right] {angle};
    \draw[->] (0,0) -- (0,1.15) node[above] {magnitude};
    \node[font=\bfseries] at (3.5,1.25) {Angular domain};
    \draw[farblue,thick]
      plot[smooth] coordinates {(0.3,0.02)(0.9,0.03)(1.3,0.08)(1.55,0.95)
      (1.8,0.08)(2.5,0.02)(3.2,0.04)(3.55,1.0)(3.9,0.05)
      (4.8,0.02)(5.3,0.06)(5.65,0.9)(5.95,0.05)(6.7,0.02)};
    \draw[nearorange,thick]
      plot[smooth] coordinates {(0.3,0.03)(0.8,0.08)(1.2,0.35)(1.6,0.55)
      (2.0,0.32)(2.5,0.08)(3.0,0.15)(3.5,0.48)(4.0,0.28)
      (4.6,0.1)(5.1,0.22)(5.65,0.52)(6.1,0.24)(6.7,0.05)};
    \node[farblue] at (1.2,1.03) {far};
    \node[nearorange] at (5.9,0.67) {near: spread};

    % Right axes
    \begin{scope}[xshift=8.3cm]
      \draw[->] (0,0) -- (7.2,0) node[right] {polar grid};
      \draw[->] (0,0) -- (0,1.15) node[above] {gain};
      \node[font=\bfseries] at (3.5,1.25) {Polar domain};
      \foreach \x/\h in {1.0/0.55,2.1/0.92,3.7/0.68,5.0/1.0,6.1/0.48} {
        \draw[polarred,very thick] (\x,0) -- (\x,\h);
        \fill[polarred] (\x,\h) circle (1.4pt);
      }
      \node[polarred] at (3.7,1.03) {few physical paths};
    \end{scope}
  \end{tikzpicture}
  \caption{Energy spread and polar sparsity, adapted from
  Figs.~2 and~8 of \cite{cui2022}.}
  \label{fig:sparsity}
\end{figure}

Figure~\ref{fig:sparsity} captures the key motivation selected by the
group. In the angular domain, a far-field path forms a narrow peak, while
a near-field path occupies many bins. In the polar domain, each path is
represented by an angle--distance pair and the channel again contains only
a few significant coefficients. This restored sparsity is what makes
low-pilot compressed sensing practical.

\tightsection{Dictionary Design Objective}

The polar grid should not contain highly similar columns. The paper
therefore designs its samples to reduce
\begin{equation}
  \mu=\max_{p\neq q}
  \left|\fieldvec{b}^{H}(\theta_p,r_p)
              \fieldvec{b}(\theta_q,r_q)\right|,
  \label{eq:coherence}
\end{equation}
because lower coherence improves the reliability of sparse support
detection.

\newpage

% ---------------------------------------------------------------------------
% Page 3: Transform matrix W
% ---------------------------------------------------------------------------
\tightsection{Design of the Polar-Domain Matrix \texorpdfstring{$W$}{W}}

The exact spherical distance makes direct grid design difficult. The
Fresnel approximation separates its phase into
\begin{equation}
  r^{(n)}-r
  \approx -\delta_n d\theta+\frac{\delta_n^2d^2(1-\theta^2)}{2r}.
  \label{eq:fresnel}
\end{equation}
The linear term describes angle; the quadratic term contains the coupled
quantity $(1-\theta^2)/r$. This yields the two sampling rules emphasized in
slides 9--17.

\tightsection{Angular Sampling on Distance Rings}

Locations satisfying
\begin{equation}
  \frac{1-\theta^2}{r}=\frac{1}{\rho}
  \label{eq:ring}
\end{equation}
have the same quadratic phase and lie on a \emph{distance ring} $\rho$.
Within one ring, coherence is governed by the same linear phase as in a
far-field Fourier dictionary. Therefore the angles are sampled uniformly:
\begin{equation}
  \theta_n=\frac{2n-N+1}{N},
  \qquad n=0,1,\ldots,N-1.
  \label{eq:angle-sampling}
\end{equation}

\tightsection{Nonuniform Distance Sampling}

For vectors at the same angle, coherence depends on the difference between
inverse distances. To keep adjacent columns below a chosen coherence
threshold, the sampled distance at angle $\theta$ follows
\begin{equation}
  r_s(\theta)=\frac{1}{s}Z_{\Delta}(1-\theta^2),
  \qquad s=0,1,2,\ldots,
  \label{eq:distance-sampling}
\end{equation}
where $Z_{\Delta}$ is determined by the array, wavelength, and desired
coherence threshold. The case $s=0$ denotes an infinite-distance
far-field ring. Thus distance is sampled uniformly in inverse distance,
not uniformly in metres.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[
      >=Latex,
      ring/.style={draw,ellipse,minimum width=#1,minimum height=1.0cm},
      sample/.style={circle,fill=polarred,inner sep=1.4pt},
      note/.style={font=\small,align=center}
    ]
    \node[draw,fill=black,minimum width=2.4cm,minimum height=0.15cm] (array) at (0,0) {};
    \node[note] at (0,-0.45) {array};
    \draw[nearorange,thick] (0,0.1) arc[start angle=180,end angle=0,x radius=2.0cm,y radius=0.65cm];
    \draw[nearorange!75,thick] (0,0.1) arc[start angle=180,end angle=0,x radius=3.1cm,y radius=1.05cm];
    \draw[nearorange!50,thick] (0,0.1) arc[start angle=180,end angle=0,x radius=4.2cm,y radius=1.45cm];
    \foreach \x/\y in {0.7/0.48,1.5/0.69,2.4/0.74,3.3/0.61,
                       1.0/0.74,2.1/1.10,3.5/1.15,4.8/0.86,
                       1.4/0.96,2.8/1.48,4.6/1.52,6.2/1.05}
      \node[sample] at (\x,\y) {};
    \node[note,nearorange] at (6.0,1.85)
      {uniform angles\\on each ring};
    \draw[->,nearorange] (5.3,1.7) -- (4.6,1.52);
    \node[note] at (8.7,0.8)
      {ring spacing is\\nonuniform in distance\\and uniform in $1/r$};
    \draw[->] (7.6,0.85) -- (6.2,1.05);
  \end{tikzpicture}
  \caption{Conceptual distance-ring sampling used to construct
  $\fieldvec{W}$.}
  \label{fig:rings}
\end{figure}

\tightsection{Matrix Construction}

Each ring produces
\begin{equation}
  \fieldvec{W}_s=
  [\fieldvec{b}(\theta_0,r_{s,0}),\ldots,
   \fieldvec{b}(\theta_{N-1},r_{s,N-1})],
\end{equation}
and $\fieldvec{W}=[\fieldvec{W}_0,\ldots,\fieldvec{W}_{S-1}]
\in\mathbb{C}^{N\times NS}$. The $s=0$ far-field ring makes the Fourier
dictionary a special case.

\newpage

% ---------------------------------------------------------------------------
% Page 4: Algorithms
% ---------------------------------------------------------------------------
\tightsection{Near-Field Channel Estimation Algorithms}

After analog combining, the noise is colored. The paper first applies a
Cholesky-based pre-whitening transform and obtains the multi-subcarrier
model
\begin{equation}
  \overline{\fieldvec{Y}}
  =\overline{\fieldvec{\Phi}}\fieldvec{H}^{P}
   +\overline{\fieldvec{N}},
  \qquad
  \overline{\fieldvec{\Phi}}
  =\fieldvec{D}^{-1}\fieldvec{A}\fieldvec{W}.
  \label{eq:whitened}
\end{equation}
The rows of $\fieldvec{H}^{P}$ share a common sparse support because path
angles and distances are common across subcarriers.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[
      >=Latex,
      box/.style={draw,rounded corners,minimum width=5.55cm,
                  minimum height=0.78cm,align=center,font=\small},
      arrow/.style={->,thick}
    ]
    \node[box,fill=softgray] (input) at (0,0)
      {Pilots, combiner, and polar dictionary};
    \node[box,fill=farblue!10,below=0.35cm of input] (white)
      {Pre-whiten observations and sensing matrix};
    \node[box,fill=farblue!14,below=0.35cm of white] (psomp)
      {P-SOMP: support search, least squares,\\residual update, channel synthesis};
    \node[box,fill=nearorange!13,right=0.65cm of psomp] (psigw)
      {P-SIGW: initialize from P-SOMP,\\refine angle, distance, and gain};
    \node[box,fill=darkgreen!12,below=0.55cm of psigw] (output)
      {Off-grid channel estimate};
    \draw[arrow] (input) -- (white);
    \draw[arrow] (white) -- (psomp);
    \draw[arrow] (psomp) -- (psigw);
    \draw[arrow] (psigw) -- (output);
  \end{tikzpicture}
  \caption{Combined workflow of the two algorithms emphasized in the
  group presentation.}
  \label{fig:algorithms}
\end{figure}

\subsection{On-Grid P-SOMP}

P-SOMP extends simultaneous OMP from the angular dictionary to
$\fieldvec{W}$. It proceeds as follows:
\begin{enumerate}
  \item construct $\fieldvec{W}$ and pre-whiten the measurements;
  \item initialize the residual and an empty support set;
  \item select the polar atom with the largest summed correlation across
  subcarriers;
  \item estimate gains by least squares and update the residual;
  \item repeat for the detected paths and synthesize the channel.
\end{enumerate}
Because $s=0$ represents infinite distance, P-SOMP also works for
far-field paths. Its weakness is grid mismatch: real angles and distances
are continuous and rarely coincide exactly with sampled atoms.

\subsection{Off-Grid P-SIGW}

P-SIGW uses P-SOMP only for initialization. It constructs a small steering
matrix from the detected paths and minimizes the whitened reconstruction
error
\begin{equation}
  \min_{\fieldvec{\theta},\fieldvec{r},\fieldvec{G}}
  \left\|
  \overline{\fieldvec{Y}}
  -\widetilde{\fieldvec{\Phi}}(\fieldvec{\theta},\fieldvec{r})
   \fieldvec{G}
  \right\|_F^2.
  \label{eq:psigw}
\end{equation}
Alternating updates refine angle and inverse distance, followed by a
least-squares gain update. This directly estimates continuous path
parameters and removes the resolution floor of P-SOMP.

\tightsection{Trade-Off}

P-SOMP is simpler but bounded by grid resolution. P-SIGW corrects off-grid
mismatch and improves NMSE at the cost of iterative optimization.

\newpage

% ---------------------------------------------------------------------------
% Page 5: Results and conclusion
% ---------------------------------------------------------------------------
\tightsection{Simulation Results}

The distance experiment uses $N=256$ antennas, a 100 GHz carrier,
SNR $=10$ dB, and pilot length $P=32$. The corresponding Rayleigh distance
is about 100 m. Figure~\ref{fig:nmse-distance} redraws the principal trends
from Fig.~10 of the paper rather than reproducing its image.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[x=0.075cm,y=0.22cm,font=\small]
    \draw[->] (0,0) -- (125,0) node[right] {distance (m)};
    \draw[->] (0,-25) -- (0,1) node[above] {NMSE (dB)};
    \foreach \x in {20,40,60,80,100,120}
      \draw (\x,0.4) -- (\x,-0.4) node[below] {\x};
    \foreach \y in {-5,-10,-15,-20,-25}
      \draw (0.8,\y) -- (-0.8,\y) node[left] {\y};
    \draw[dashed,thick] (100,0) -- (100,-25);
    \node[rotate=90,anchor=south] at (100,-12.5) {Rayleigh distance};

    \draw[polarred,very thick]
      plot[smooth] coordinates {(5,-19)(10,-20)(20,-20.2)(40,-20.3)
      (60,-20.3)(80,-20.3)(100,-20.2)(120,-20.0)};
    \draw[nearorange,thick]
      plot[smooth] coordinates {(5,-13)(10,-14)(20,-14.5)(40,-14.8)
      (60,-15)(80,-15)(100,-15)(120,-15)};
    \draw[farblue,thick]
      plot[smooth] coordinates {(5,-5)(10,-8)(20,-10.5)(40,-12.5)
      (60,-13.5)(80,-14.2)(100,-15)(120,-15.5)};
    \draw[darkgreen,thick,dash pattern=on 4pt off 2pt]
      plot[smooth] coordinates {(5,-4)(10,-7)(20,-9)(40,-11)
      (60,-12.5)(80,-13.8)(100,-15)(120,-16)};
    \draw[gray,thick] (5,-2.5) -- (120,-2.5);

    \node[polarred,anchor=west] at (18,-21.8) {P-SIGW};
    \node[nearorange,anchor=west] at (55,-16.7) {P-SOMP};
    \node[farblue,anchor=west] at (104,-17.0) {angular on-grid};
    \node[darkgreen,anchor=west] at (67,-12.2) {angular off-grid};
    \node[gray,anchor=west] at (103,-4.0) {LS};
  \end{tikzpicture}
  \caption{Trend-focused redraw of NMSE versus distance from
  \cite[Fig.~10]{cui2022}.}
  \label{fig:nmse-distance}
\end{figure}

\tightsection{Interpretation}

Inside the Rayleigh distance, angular-domain methods suffer severe model
mismatch because a spherical path is not sparse in angle. Their NMSE
improves only as distance increases and the wavefront becomes nearly
planar. P-SOMP is much less sensitive to distance because its dictionary
contains the required angle--distance atoms. P-SIGW is best because it
also removes the polar-grid quantization error.

The other experiments selected by the group support the same conclusion.
As SNR increases, near-field polar methods continue improving while
mismatched angular methods approach an error floor. In the far-field
setting, the polar methods match the angular baselines and become
slightly better at high SNR, because the Fresnel approximation is more
accurate than the planar-wave one. Increasing pilot length improves all
compressed-sensing estimators, but the gain is much larger when the
representation matches the propagation physics.

\tightsection{Conclusion}

XL-MIMO does not destroy physical channel sparsity; it destroys
\emph{angle-only} sparsity. Uniform angle sampling on distance rings and
nonuniform sampling in $1/r$ let $\fieldvec{W}$ concentrate spherical
paths. P-SOMP exploits this structure with low pilot overhead, while
P-SIGW trades extra computation for off-grid accuracy.

\renewcommand{\refname}{References}
\begin{thebibliography}{1}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\footnotesize

\bibitem{cui2022}
M. Cui and L. Dai, ``Channel estimation for extremely large-scale MIMO:
Far-field or near-field?'' \emph{IEEE Trans. Commun.}, vol. 70, no. 4,
pp. 2663--2677, Apr. 2022, doi: 10.1109/TCOMM.2022.3146400.

\end{thebibliography}

\newpage

% ---------------------------------------------------------------------------
% Page 6: reserved Q&A
% ---------------------------------------------------------------------------
\section*{Q\&A}
\addcontentsline{toc}{section}{Q\&A}

\noindent
\textit{This page is reserved for questions and answers. Replace the
placeholders below when the final Q\&A content is available.}

\vspace{1.2em}

\noindent\textbf{Question 1.} \rule{0.78\textwidth}{0.4pt}

\vspace{0.7em}
\noindent\textbf{Answer.}\\[0.35em]
\rule{\textwidth}{0.4pt}\\[1.05em]
\rule{\textwidth}{0.4pt}\\[1.05em]
\rule{\textwidth}{0.4pt}

\vspace{1.5em}

\noindent\textbf{Question 2.} \rule{0.78\textwidth}{0.4pt}

\vspace{0.7em}
\noindent\textbf{Answer.}\\[0.35em]
\rule{\textwidth}{0.4pt}\\[1.05em]
\rule{\textwidth}{0.4pt}\\[1.05em]
\rule{\textwidth}{0.4pt}

\vspace{1.5em}

\noindent\textbf{Question 3.} \rule{0.78\textwidth}{0.4pt}

\vspace{0.7em}
\noindent\textbf{Answer.}\\[0.35em]
\rule{\textwidth}{0.4pt}\\[1.05em]
\rule{\textwidth}{0.4pt}\\[1.05em]
\rule{\textwidth}{0.4pt}

\vfill
\begin{center}
  \textit{Additional questions may be added while retaining this page as
  the final section of the report.}
\end{center}

\end{document}
